\documentclass{homework}
\course{Math 7851}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
  Bundle and save!
  \byline{Progressive Insurance}
\end{inspiration}

\section{Terminology}

\begin{problem}
What is a \textbf{smooth manifold}?
\end{problem}

\begin{problem}
What is a \textbf{vector bundle}?
\end{problem}

\section{Numericals}

\begin{problem}
  Let $E_n \to S^2$ be the complex line bundle corresponding to the
  ``clutching construction'' using $z \mapsto z^n$.

  The tensor product $E_n \otimes E_m$ is itself a complex line bundle
  --- which one is it?
\end{problem}

\begin{problem}
  Regarding $S^2$ as $\mathbb{C}P^1$, we can interpret $TS^2$ as a complex line bundle.

  Find $n$ so $TS^2 \cong E_n$.
\end{problem}

\begin{problem}
  Consider the complex line bundle $H = E_1$, the \textbf{canonical line bundle} over  $\mathbb{C}P^1$.

  Show that
  \[
    (H \otimes H) \oplus \underline{\mathbb{C}} \cong H \oplus H.
  \]
\end{problem}

\section{Exploration}

\begin{problem}
  Describe a nontrivial line bundle over $S^1$.\label{mobius-bundle}
\end{problem}

\begin{problem}
  Consider the bundle $E \to S^1$ from \ref{mobius-bundle}.  Regarding
  $S^1 \subset \mathbb{C}$, let $f : S^1 \to S^1$ be the doubling map
  $f(z) = z^2$.

  Is the bundle $f^\star E$ trivial?
\end{problem}

\section{Prove or Disprove and Salvage if Possible (PODASIP)}

\textit{You may not have met these PODASIP-style problems before.
  What follows are statements which may be ``true'' or ``false.''  If
  the statement is true, you must provide a proof.  If the statement
  is false, explain why it is false, then fix the statement and
  finally supply a proof for the repaired statement.}

\begin{problem}
  The sphere $S^n$ admits a nowhere-vanishing vector field.
\end{problem}

\end{document}
