\documentclass{homework}
\input{preamble}
\author{Jim Fowler}
\course{Math 7852}
\date{Week 1: Manifolds}

\begin{document}
\maketitle

Each week, I'll post a few notes on what to read, and I'll try to
\textbf{emphasize} the key topics we plan to cover each week.

For this week, from Milnor--Stasheff's \textit{Characteristic
  Classes}, read the first chapter entitled ``Smooth Manifolds.''
This course is a course in differential topology, and \textbf{smooth
  manifolds} are the central object of our study.  Recall that a
manifold is a topological space that is locally Euclidean but can be
``globally'' more complicated.  A \textit{smooth} manifold is a
topological manifold endowed with a \textbf{smooth structure} --- that
is, a manifold along with some additional data that allows for
differential calculus on that manifold.  For example, we can take
\textbf{derivatives} and we can speak of \textbf{tangent vectors} and
build \textbf{tangent bundles}.

To put all this in some broader context: a topological manifold could
support \textit{different} smooth structures.  Or you may be familiar
with piecewise linear (PL) manifolds, which are topological manifolds
together with a piecewise linear structure on it, i.e., there is an
atlas with with PL transition functions.  A smooth structure gives
rise to a PL structure, but not every PL manifold is smoothable.

Another reference is \textit{Topology from the Differentiable
  Viewpoint} by Milnor, which we'll use to discuss \textbf{regular
  values} and \textbf{critical values}.  We will see later that
\textbf{transversality} generalizes the notion of regular values.

\end{document}
